\documentclass{resume}

\newcommand{\en}[1]{#1}
\newcommand{\zh}[1]{}
\usepackage{enumitem}
\zh{\usepackage{xeCJK}}
% \zh{\setCJKmainfont{SourceHanSansHWSC-Regular}}
% \zh{\setCJKsansfont{SourceHanSansHWSC-Regular}}
% \zh{\setCJKmonofont{SourceHanSansHWSC-Regular}}

\begin{document}

\name{\en{Qinyang Huang}\zh{黄沁洋}}
\basicInfo{
      \phone{(919)841-2013}
      \email{qhuang26@ncsu.edu}
      \homepage[LinkedIn/qinyang]{https://www.linkedin.com/in/qinyang-huang-931b531a6/}
      \github[Bazinga-0411]{https://github.com/Bazinga-0411}
}

% \section{\en{Summary}\zh{教育经历}}
% \en{Financial Mathematics Graduate Student with over 3 years of hands-on experience in data analysis as well as market trading. Skilled in 
% data visualization, modeling, and machine learning, using software tools including Python, SQL, and R.}
\section{\en{Education}\zh{教育经历}}
\en{\datedsubsection{\textbf{\href{https://ncsu.edu}{Global Association of Risk Professionals (GARP)}}}{05/2021}}
\zh{\datedsubsection{\textbf{\href{https://ncsu.edu}{北卡州立}}, 本科}{2023/09 -- 2025/01}}
\begin{itemize}[]

      \item FRM Program - Passed FRM Exam Part I
\end{itemize}
\en{\datedsubsection{\textbf{\href{https://ncsu.edu}{North Carolina State University}}}{08/2023 -- 12/2024}}
\zh{\datedsubsection{\textbf{\href{https://ncsu.edu}{北卡州立}}, 本科}{2023/09 -- 2025/01}}
\begin{itemize}[]

      \item \en{Master of Financial Mathematics (GPA: 4.0/4.0)}
            \zh{工商管理，完成计算机网络、数据库、金融、高等数学}
\end{itemize}

\en{\datedsubsection{\textbf{\href{http://en.usst.edu.cn/}{University of Shanghai for Science and Technology}}}{09/2018 -- 06/2022}}
\zh{\datedsubsection{\textbf{\href{http://www.usst.edu.cn/main.htm}{上海理工大学}}, 本科}{2018/09 -- 2022/06}}
\begin{itemize}[]

      \item \en{Bachelor of Business Administration(3.59/4.0)}
            \zh{工商管理，完成计算机网络、数据库、金融、高等数学}
\end{itemize}
% \vspace{2 mm}


\section{\en{Work Experience}\zh{工作经历}}
\en{\datedsubsection{\textbf{\href{https://zdb.pedaily.cn/enterprise/show102413/}{Shanghai XUANLIN Capital Management LLC}}, Shanghai, China}{12/2021 -- 04/2023}}
\zh{\datedsubsection{\textbf{\href{https://zdb.pedaily.cn/enterprise/show102413/}{悬铃资产管理有限公司}}}{12/2021 -- 04/2023}}

\en{\role{Fulltime}{Investment Team}}
\zh{\role{全职}{投资组}}

\begin{itemize}
      \item \en{Oversaw daily subscriptions for newly listed stocks and actively engaged in the declaration and execution of off-exchange private 
      placement projects, consistently yielding a 10\% annual return.}
            \zh{场外业务,打新,新股申购,询价转让,定向增发}
      \item \en{Extracted data from the Wind database and executed comprehensive data analysis, contributing to the development of a targeted arbitrage strategy for convertible bonds.}
            \zh{学习如何编写期权定价的python代码}
      \item \en{Monitored market conditions to ensure compliance with internal guidelines and regulatory standards. Developed relationships with external brokers and vendors to optimize trading}
            \zh{学习如何编写期权定价的python代码}
\end{itemize}

% \en{\datedsubsection{\textbf{\href{https://www.cfsc.com.cn/}{Huaxin Securities Limited Liability Company}}, Shanghai, China}{09/2021 -- 11/2021}}
% \zh{\datedsubsection{\textbf{\href{https://www.cfsc.com.cn/}{华鑫证券有限责任公司}}}{09/2021 -- 11/2021}}

% \en{\role{Intern}{Data Analytics Intern}}
% \zh{\role{实习}{数据处理组}}

% \begin{itemize}
%       \item \en{Apply Excel to extract data from Wind Database and provide insightful suggestions}
%             \zh{用Excel从Wind数据库中提取数据，提供数据分析建议}
%       \item \en{Collect the data using Wind News API for report}
%             \zh{使用Wind新闻API收集数据，用于报告}
% \end{itemize}

% \en{\datedsubsection{\textbf{\href{https://www.liepin.com/}{Lie Pin.com (Chinese version of LinkedIn)}}, Shanghai, China}{05/2020 -- 07/2020}}
% \zh{\datedsubsection{\textbf{\href{https://www.liepin.com/}{猎聘网}}}{05/2020 -- 07/2020}}
%

% \en{\role{Intern}{Finance Recruiter Intern}}
% \zh{\role{实习}{金融组HR部门}}
%

% \begin{itemize}
%       \item \en{Provide support for a internal talent resume database for better matching the employer candidate and employee}
%             \zh{为内部人才库提供支持，更好地匹配雇主候选人和员工}
%       \item \en{Give HR interview and first feedback for matching candidate}
%             \zh{为候选人进行HR面试和初步反馈}
% \end{itemize}

%

\section{\en{Project}\zh{项目}}
\begin{itemize}[parsep=0.25ex]
     
            \item \datedsubsection{\en{\href{https://github.com/Bazinga-0411/Market-Risk-sp24}{\textbf{Market Risk Analysis of American Express (AXP) and S\&P 500 ETF (SPY) }} }     }{02/2024 -- 04/2024}
            \begin{itemize}
                  \item Data Acquisition: Sourced daily closing price data for AXP and SPY from January 1, 2021, to March 8, 2024, utilizing Python and the yfinance library, to ensure accurate and reliable input for subsequent analysis.
                  \item Volatility Analysis Using GARCH (1,1): Calculated daily log returns based on closing prices of AXP and SPY, then applied the GARCH (1,1) model to estimate asset volatility.
                  \item Statistical Model Validation: Conducted comprehensive robustness checks, including evaluating the Log-Likelihood, AIC, BIC, and p-value statistics. This process validated the GARCH model’s effectiveness in accurately capturing the volatility dynamics, ensuring the reliability of our volatility estimates.
                  \item Risk Metrics Calculation: Derived the one-day 99\% Value at Risk (VaR) and Expected Shortfall (ES) for AXP, SPY, and their combined portfolio using historical simulation based on daily log returns.
                  \item RAROC Analysis: Utilized Python to compute the Risk-Adjusted Return on Capital (RAROC) for AXP, SPY, and their portfolio. 
                  
            \end{itemize}
            \item \datedsubsection{\href{https://github.com/Bazinga-0411/AAPL_Price_Prediction/}{\textbf{Assessing Credit Risk and Predicting Loan Defaults with XGBoost Model } }}{08/2023 -- 12/2023}
           
            \begin{itemize}
                  \item Data Handling: Utilized the Freddie Mac single-family loan dataset encompassing 500,000 mortgage loans with 27 features (2000-2018), applying comprehensive data processing and feature selection techniques, including forward feature selection and LASSO.
                 \item Imbalance and Categorical Data: Addressed data imbalance with SMOTE and converted categorical data into booleans via one-hot encoding, ensuring data quality for model training.
                  Modeling and Optimization: Implemented and compared multiple machine learning models (Logistic Regression, Random Forest, XGBoost), utilizing hyperparameter tuning to enhance accuracy effectively.
                  \item Outcomes: Achieved significant predictive performance, evidenced by an F-1 score of 0.93 and an AUC-ROC score of 0.98, demonstrating the model's robustness in predicting loan defaults accurately.
                  
                  

            \end{itemize}
            % \item \en{{\textbf{FIM548 Project: Lookback Call}}\href{https://github.com/Bazinga-0411/FIM548-sp24-hw3}{Bazinga/Lookback-Call-sp24}}           
            % \begin{itemize}
            % \item The aim of this mini project is to perform a risk analysis of American Express (AXP) and the S\&P 500 Index (SPY) using historical stock price data from January 1, 2021, to March 8, 2024. The project involves downloading data, calculating returns, fitting GARCH(1,1) models, and analyzing the correlation between AXP and SPY returns.
            % \end{itemize}
\end{itemize}

\section{\en{Skills}\zh{技能}}
\begin{itemize}[parsep=0.25ex]
      \item \en{\textbf{Programming Languages}:
                  Familiar with : Python (pandas, scikit-learn, numpy), SQL, R etc.}
      \item \en{\textbf{Financial Analysis}:
                  Financial Risk Management First Level Passed, Baruch C++ Finance Engineering Passed.}

      \item \en{\textbf{Data Analysis}: Familiar with using Python Pandas to deal with big Data. Using Large Language Model to do Prompt Engineering.}

      \item \en{\textbf{Machine Learning}:
            Familiar with Machine Learning and Statistics Model for Data Analysis.}
            \zh{\textbf{机器学习}:
                  熟悉经典机器学习算法。}
           

\end{itemize}

% \section{\en{Miscellaneous}\zh{证书}}
% \begin{itemize}
%       \item \en{Completion of FRM(Financial Risk Manager) level 1}
%             \zh{金融风险管理师从业一级通过。}
           
%       \item \en{Completion of Baruch C++ for Finance Engineering}
%             \zh{巴塞尔大学C++金融工程课程通过。}
           
      % \item \en{Completion of Coursera Introduction to Python, Using Python to Analyze Data, Data Structure, Analysis of Algorithms}
      %       \zh{Coursera Python入门、Python数据分析、数据结构、算法分析课程通过。}
           
      % \item \en{In preparation of CFA level 1, Coursera Introduction to Artificial Intelligence}
      %       \zh{CFA一级考试准备中。学习Coursera AI入门课程。}
           
% \end{itemize}

\end{document}